### 2025-07-10 actuarial.qmd
20250709 - videos
20250710 - video citations

@@

@TPS2017 provides a video of sports pundits, Stephen A. Smith and Skip Bayless, making bold statements and incorrect predictions, in @fig-video-sports-pundits:

>>>>

@fig-video-sports-pundits is a video of sports pundits, Stephen A. Smith and Skip Bayless, making bold statements and incorrect predictions [@TPS2017]:

@@

### 2025-07-10 cognitive-bias.qmd
20250709 - videos
20250710 - video citations

@@

A video from @GetUpESPN2021 (archived at <https://perma.cc/JW8E-KV2C>) of Kyle Pitts drawing comparisons to the LeBron James of Tight Ends is in @fig-kyle-pitts:

>>>>

@fig-kyle-pitts is a video from @GetUpESPN2021 (archived at <https://perma.cc/JW8E-KV2C>) of Kyle Pitts drawing comparisons to the LeBron James of Tight Ends:

@@

### 2025-07-10 fantasy-football.qmd
20250709 - videos
20250710 - video citations

@@

A video that provides a brief introduction to American football is in @fig-football-intro [@Ly2015]:

@@

@@

A video that provides a brief introduction to fantasy football is in @fig-fantasy-football-intro [@NFLFantasy2020]:

>>>>

@fig-football-intro is a video that provides a brief introduction to American football [@Ly2015]:

@@

@@

@fig-fantasy-football-intro is a video that provides a brief introduction to fantasy football [@NFLFantasy2020]:

@@

### 2025-07-10 intro.qmd
20250709 - videos
20250710 - video citations

@@

A video of Professor Benjamin Motz that describes the value of teaching statistics through the lens of fantasy football is in @fig-video-motz [@NFL2014]:

>>>>

@fig-video-motz is a video of Professor Benjamin Motz that describes the value of teaching statistics through the lens of fantasy football [@NFL2014]:

@@

### 2025-07-10 sports-cognitive-psychology.qmd
20250709 - videos
20250710 - video citations

@@

For instance, there is a [2015 video clip](https://streamable.com/1hw8) of a football commentator, Mike Patrick, making fun of people who compile statistics for informing decision-making in football, calling the people who compile the numbers "guys who wear socks with flip-flops" in @fig-football-commentator [@ABC2015], suggesting that people who compile analytics to make recommendations in football are out of touch with the realities of football and do not have the same on-the-field understanding as the coaches and players.
The full game is [here](https://www.youtube.com/watch?v=1L9D2rp0mk8) [@ABC2015a].

>>>>

As an example of people dismissing analytics, @fig-football-commentator is a [2015 video clip](https://streamable.com/1hw8) of a football commentator, Mike Patrick, making fun of people who compile statistics for informing decision-making in football, calling the people who compile the numbers "guys who wear socks with flip-flops" [@ABC2015].
His characterization suggests he believes that people who compile analytics to make recommendations in football are out of touch with the realities of football and do not have the same on-the-field understanding as the coaches and players.
The full game is [here](https://www.youtube.com/watch?v=1L9D2rp0mk8) [@ABC2015a].

@@
